Online {\IterComp}

### 2017-11-16 results.tex
updates plot
updates result

We also evaluate the actual cost perceived by the user when applying online iterative compilation.
To this end we used the architecture described in Section~\ref{sec:oic-infra} with the search based on genetic algorithm.
The results suggest that the proposed approach can be profitable in real-world online scenarios.
For the \WCRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.
For the \WPRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.

>>>>

We also evaluate the actual cost perceived by the user when applying online iterative compilation.
To this end we used the architecture described in Section~\ref{sec:oic-infra} with the search based on genetic algorithm.
Our results provide evidence that the proposed approach is profitable in real-world online scenarios.
Figure~\ref{fig:deployment_cost} shows, for each benchmark and configuration, the profitability of the final optimization sequence
selected by the search (as in Figure~\ref{fig:speedups}) but also the average profitability/cost experienced by the user throughout the search process (labeled as [Live]),
which takes into account the overhead of the work profiling.

A Search Driver based on genetic algorithm is able to focus the search on promising optimization sequences, reducing the risk of
executing sub-optimal versions of the program as the search evolves through generations.
Although the user may experience slowdown during the optimization process, due to overheads or by executing sub-optimal versions of the program, after the first generation,
the optimization sequences produced tend to overcome these costs, with their benefits surpassing the profiling overheads.

For the \WCRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.
For the \WPRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.

%\begin{figure*}[t]
%  \centering
%  \subfigure[Opt-Profiling]{\includegraphics[width=0.3\textwidth]{figs/Opt-Profiling-deployment.pdf}}
%  \subfigure[WC-Relax-5]{\includegraphics[width=0.3\textwidth]{figs/WC-Relax-5-deployment.pdf}}
%  \subfigure[WP-Relax-5]{\includegraphics[width=0.3\textwidth]{figs/WP-Relax-5-deployment.pdf}}
%  \caption{deployment cost.}
%  \label{fig:deployment_cost}
%\end{figure*}
